The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-11-25 donde.tex
fix order of level in potential outcomes in tot-tut table

If we could perfectly measure present bias \textcolor{teal}{and sophistication}, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment). %If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.
If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is positive. This is because among the group of non-takers, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.

>>>>

If we could perfectly measure present bias and sophistication, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment). %If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.
If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is positive. This is because among the group of non-takers, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
